A comparison of design-based and model-based approaches for finite population spatial data.

### 2021-10-19 inst/manuscript/manuscript.Rmd
added supplementary material

@@

We used a crossed design with the simulation parameters given in Table \ref{tab:parmtab} for a total of 36 scenarios. All scenarios used exponential correlation with an effective range of $\sqrt{2}$ for $N = 900$ response values simulated on the unit square in either random locations (Layout = Random) or gridded locations (Layout = Gridded). The mean for the spatial process generating the response was set to zero.

@@

files <- list.files(path = here("inst", "output", "sims914"), pattern = "*.csv", full.names = TRUE)

>>>>

Add sentence about bias.
Add sentence about user functions.

@@

We used a crossed design with the simulation parameters given in Table \ref{tab:parmtab} for a total of 36 scenarios. All scenarios used exponential correlation with a  $\sqrt{2} / 3$ for $N = 900$ response values simulated on the unit square in either random locations (Layout = Random) or gridded locations (Layout = Gridded). The range was chosen so that the decayed to nearly zero at the largest distance possible in the domain, $\sqrt{2}$, otherwise known as the "effective" range (for the exponential covariance, the effective range is $3\phi$). The mean for the spatial process generating the response was set to zero.

@@

files <- list.files(path = here("inst", "output", "simulation_summary"), pattern = "*.csv", full.names = TRUE)

### 2021-10-19 inst/manuscript/manuscript.tex
added supplementary material

We used a crossed design with the simulation parameters given in Table
\ref{tab:parmtab} for a total of 36 scenarios. All scenarios used
exponential correlation with an effective range of \(\sqrt{2}\) for
\(N = 900\) response values simulated on the unit square in either
random locations (Layout = Random) or gridded locations (Layout =
Gridded). The mean for the spatial process generating the response was
set to zero.

>>>>

We used a crossed design with the simulation parameters given in Table
\ref{tab:parmtab} for a total of 36 scenarios. All scenarios used
exponential correlation with a \(\sqrt{2} / 3\) for \(N = 900\) response
values simulated on the unit square in either random locations (Layout =
Random) or gridded locations (Layout = Gridded). The range was chosen so
that the decayed to nearly zero at the largest distance possible in the
domain, \(\sqrt{2}\), otherwise known as the ``effective'' range (for
the exponential covariance, the effective range is \(3\phi\)). The mean
for the spatial process generating the response was set to zero.
